---
title: "Chapter 1"
output:
  html_document:
    df_print: paged
---

## Intro
ref for correct solutions:
http://rstudio-pubs-static.s3.amazonaws.com/393789_2f70cbc28a3f4c4a81ec4b10123d5324.html

## Example 1.2. Xelox in patients with advanced gastric cancer

```{r}
library (asaur)
gastricXelox[23:27,]
```



The first column is the patient (row) number. The second is a list of survival
times, rounded to the nearest week, and the third is “delta”, which is the censoring
indicator.

## Example 1.3. Pancreatic cancer in patients with locally advanced or metastatic
disease

```{r}
head(pancreatic)
```

Patient #3, a patient with locally advanced disease (stage = “LA”),
entered the study on February 3, 2006. That person was found to have progressive
disease on August 2 of that year, and died on January 19 of the following year.

## Example 1.4 Survival prospects of prostate cancer patients with high-risk disease
For each patient we have grade (poorly or moderately differentiated), age
of diagnosis (66-70, 71-75, 76-80, and 80+), cancer stage ( T1c if screen-diagnosed
using a prostate-specific antigen blood test, T1ab if clinically diagnosed without
screening, or T2 if palpable at diagnosis), survival time (days from diagnosis to
death or date last seen), and an indicator (“status”) for whether the patient died of prostate cancer (status = 1), died of some other cause (status = 2), or was
still alive at the date last seen (status = 0). The simulated data set matches the
original in the number of patients in each of the two grades, three stages, and four
age groups (24 categories).

```{r}
prostateSurvival[88:95,]
```

## Example 1.5. Comparison of medical therapies to aid smokers to quit

```{r}
pharmacoSmoking[1:6, 2:8]
```

The variable “ttr” is the number of days without smoking (“time to relapse”), and
“relapse=1” indicates that the subject started smoking again at the given time. The
variable “grp” is the treatment indicator, and “employment” can take the values “ft”
(full time), “pt” (part time), or “other”. The primary objectives were to compare the
two treatment therapies with regard to time to relapse, and to identify other factors
related to this outcome.

Example 1.6. Prediction of survival of hepatocellular carcinoma patients using
biomarkers

```{r}
hepatoCellular[c(1, 2, 3, 65, 71),c(2, 3, 16:20, 24, 47)]
```

The survival outcomes are “OS” (overall survival) and “RFS” (recurrence-free survival),
and the corresponding censoring indicators are “Death” and “Recurrence”.

## Exercises
### Ex 1.1

- Patient 1:
  - survival time --> 5 years
  - censoring --> 1
- Patient 2:
  - survival time --> 5 years
  - censoring --> 1
- Patient 3:
  - survival time --> 4 years
  - censoring --> 0
- Patient 4:
  - survival time --> 3 years
  - censoring --> 0
- Patient 5:
  - survival time --> 1 years
  - censoring --> 0

### Ex 1.2

For the “gastricXelox” data set, use R to determine how many patients had the
event (death or progression), the number of person-weeks of follow-up time, and
the event rate per person-week.

```{r}
# how many patients had the
# event (death or progression)
sum(gastricXelox$delta)

# the number of person-weeks of follow-up time
table(gastricXelox$timeWeeks)

#the event rate per person-week.
table(gastricXelox$delta, gastricXelox$timeWeeks)
```

  